\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-25 paper.tex
Reword game theory

\subsubsection{Registrar}
Registrars have access to create and maintain registration contracts, a lookup table of participants in decentralized data marketplace.

@@

Brokers certify session keys as well. Only one session key can be signed for each product, so data providers cannot fake a session key to deceive consumers. To certify a session key $k$, the data provider first blinds the session key with broker's public key from registration contract and sends $Blind(k)$ to the broker. The broker signs it and returns the signature $Sign(Blind(k))$ back, then the data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.

@@

\subsection{Trading}
Once a consumer subscribe to certain streaming data that is generated pays a subscription fee to the purchase contract, he/she is added to the consumers list automatically by the smart contract.

@@

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaction among game players. If we can ensure Nash Equilibrium of decentralized data marketplace exists at a certain acceptable range, then we can promise the sustainability of decentralized data marketplace. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied to data pricing. We employed repeated games to build our game theory model. Repeated games fits the scenario of data subscription.

@@

According to \textbf{assumption(\ref{rational_man})}, we learn that few consumers would take malicious actions in this system, since all the consumers are rational.

\textbf{Assumption(\ref{monopoly})} implies there is no other data providers providing the same product in the data marketplace. In this way, we can consider each provider's behavior independently. That means this decision tree represents the behavior of only one data provider.

From \textbf{assumption(\ref{51_in_group})}, we derive that one of any consumer in that group launches voting for stopping buying data (in other words, the consumer announces the data quality is not acceptable), they would succeed in rejecting the processing subscription.

\textbf{Assumption(\ref{1_in_51})}  implies if unacceptably low accuracy data are delivered to consumers, the examiner will spread this information out.

Based on the description above, the discounted sum of payoff for our repeated game is
\begin{equation} \label{payoff}
    \sum_{i=0}^{m - 1}{\beta^{in}\cdot [(\sum_{j=0}^{n - 1} \beta^j \cdot P_s) - C_{maintain}]}
\end{equation}

@@

Substitute Eq. (\ref{sub_fee}) and Eq. (\ref{C_mtn}) into Eq. (\ref{payoff}). We can derive an equation illustrating the market mechanism of the subscription trading policy we used under the decentralized data marketplace. First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is much less than moderate quality data. Second the great deficit at high accuracy is mostly derived by the rapid increasing of maintenance cost. Thus, if the maintenance fee to achieve decent data quality is under a fair price range, then data provider will automatically provide data with high enough data quality under our assumptions.

\section{\normalsize\textbf{Future Work}}
%Data Auction
The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers. While there has been many auction models\cite{BigPicDataMarket} in several areas, there has been minimal research on third-party auction platforms. Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers. However, the auction process between multiple participants and analysis of potential threats are still critical issues that need to be resolved. For the game theory model presented in this work, we assume each data provider's behavior is independent. However, normally there would be multiple data providers providing similar products (substitutions). Only one provider is taken into considerations at present.

>>>>

\subsubsection{Registrar}
Registrars have access to create and maintain Registration Contracts, a lookup table of participants in decentralized data marketplace.

@@

Brokers certify session keys as well. Only one session key can be signed for each product, so data providers cannot fake a session key to deceive consumers. To certify a session key $k$, the data provider first blinds the session key with broker's public key from Registration Contract and sends $Blind(k)$ to the broker. The broker signs it and returns the signature $Sign(Blind(k))$ back, then the data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.

@@

\subsection{Trading}
Once a consumer subscribes to certain streaming data that is generated pays a subscription fee to the purchase contract, he/she is added to the consumers list automatically by the smart contract.

@@

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaction among game players. We can ensure the sustainability of decentralized data marketplace by proving the existence of Nash Equilibrium at a certain acceptable range. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models in data pricing, and we employ repeated games which fits the scenario of data subscription to build our game theory model.

@@

According to \textbf{Assumption(\ref{rational_man})}, we learn that few consumers would take malicious actions in this system, since all the consumers are rational. \textbf{Assumption(\ref{monopoly})} implies each product is unique in the data marketplace. Therefore, each provider's behavior independently and the decision tree represents the behavior of only one data provider. From \textbf{Assumption(\ref{51_in_group})}, we derive that any consumer in that group launches voting for refund (i.e., the consumer announces the data quality is not acceptable) would succeed. \textbf{Assumption(\ref{1_in_51})}  implies if unacceptably low accuracy data are delivered to consumers, the examiner will spread this information out.

Based on the assumptions above, the discounted sum of payoff for our repeated game is
\begin{equation} \label{payoff}
    \sum_{i=0}^{m - 1}{\beta^{in}\cdot [(\sum_{j=0}^{n - 1} \beta^j \cdot P_s) - C_{maintain}]}
\end{equation}

@@

Substitute Eq. (\ref{sub_fee}) and Eq. (\ref{C_mtn}) into Eq. (\ref{payoff}). We can derive an equation illustrating the market mechanism of the subscription trading policy in the proposed decentralized data marketplace. First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is much less than moderate quality data. Second, the great deficit at high accuracy is mostly derived by the rapid increasing of maintenance cost. Thus, if the maintenance fee to achieve decent data quality is under a fair price range, then data provider will automatically provide data with high data quality under our assumptions.

\section{\normalsize\textbf{Future Work}}
%Data Auction
The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers. While there has been many auction models\cite{BigPicDataMarket} in several areas, only minimal research focus on third-party auction platforms. Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers. However, the auction process between multiple participants, analysis of potential threats and an overall game theory evaluation are still critical issues that need to be resolved.
